\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and
% 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}

% for web links
\definecolor{href}{rgb}{0.2,0.4,0.65}
\newcommand\weblink[2] {{\color{href} \href{#1}{#2}}}
\newcommand\cvskill[2] {\cvline{#1}{
\begin{minipage}[t]{%
  \linewidth}\small #2
\end{minipage}
}}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}
% only for the classic theme, if you want to change the width of your name
% placeholder (to leave more space for your address details)
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}
% required when changes are made to page layout lengths
\AtBeginDocument{\recomputelengths}

% personal data
\firstname{Gastón}
\familyname{Kleiman}
\title{Software Engineer}
\address{Virrey Arredondo 2631 5A}{C1426DZI Capital Federal, Argentina}
\phone{+54 11 4781 7018}
\mobile{+54 911 6370 1275}
\email{contact@gkleiman.com.ar}
\homepage{http://github.com/gkleiman}
\extrainfo{Nationality: Argentine with German citizenship}
% \quote{Some quote (optional)}

% uncomment to suppress automatic page numbering for CVs longer than one page

\nopagenumbers{}

\begin{document}
\maketitle

\section{Profile}
Versatile \& pragmatic developer with strong theoretical knowledge and
practical experience ranging from system programming in low--level languages to
graphic and web applications in high--level languages. Highly interested in
developing for mobile platforms (specially for Android).

Proactive, self--taught, quick--learner, goal oriented. Able to work
effectively both as part of small/big teams as well as alone on own motivation.
Deep understanding and use of FLOSS (Free Libre Open Source Software)
development methodologies and tools. Used to working under pressure and meeting
demanding deadlines. Interested in project management, experience dealing with
customers, doing the best to understand and satisfy their needs.

\section{Professional Expertise}
\begin{itemize}
\item Deep web development knowledge, ranging from back--end programming in
Ruby, Java and PHP, to front--end programming using JavaScript and HTML + CSS.
Knowledge of back--end frameworks (Rails, Tapestry) and front--end libraries
(jQuery, jQuery UI). Prefer back--end rather than front--end programming.
\item Object--oriented design and programming.
\item Strong practical knowledge of Ruby, Java, C++ and C.
\item Concurrent and network programming, including POSIX threads, BSD sockets,
  TCP/IP and POSIX IPC (Inter--Process Communication) experience.
\item Experience teaching programming with Python and using it to make small
  programs and utilities.
\item GNU/Linux systems specialist. More than 10 years of experience as user
  and administrator. Knowledge about its architecture, best--practices, shell
  scripting,  and web (Apache 2, Tomcat) \& database (MySQL) servers
  administration.
\item Practical and theoretical knowledge of networking protocols (IP, TCP/IP,
  UDP, etc.) and application protocols over IP (HTTP, SMTP, POP 3, DNS, etc.).
\item Network administration: firewalling (iptables), advanced routing, NAT.
\item Basic knowledge of the Android SDK and mobile programming.
\end{itemize}

\section{Education}
\cventry{2003 -- 2011}{MSc in Informatics Engineering}{Universidad de Buenos
Aires}{Argentina}{}{Final Project:
\weblink{https://github.com/gkleiman/wide}{wIDE} (Web Integrated Development
Environment).}
\cventry{2008 -- 2009\\ Sep \ \ \ \ \ Feb}{Research Project at the
\weblink{http://www.ibr.cs.tu-bs.de/dus/index.html}{Institute of Distributed
and Ubiquitous Systems}}{Technische Universität
Braunschweig}{Germany}{}{Participated in a research project on collaborative
transmission in wireless sensor networks using feedback based distributed
adaptive beamforming.\\Simulated and evaluated different synchronisation and
clustering approaches using MATLAB.}
\cventry{2001\\$4^{1/2}$ months}{Study Abroad}{Gymnasium
Kaiser-Friedrich-Ufer}{Hamburg}{Germany}{Lived with a German family and
attended school.}

\section{Experience}
\cvline{1999 -- now}{\textbf{Freelance Independent Software Engineer}. Working
in projects such as small websites development.}
\cventry{2009 -- 2010\\ Oct \ \ \ \ \ Jun}{Software Engineer}
{\weblink{http://www.3dgames.com.ar}{3DGames}}{Buenos Aires, Argentina}{}{%
\begin{itemize}
  \item Migrated the web site of \weblink{http://club.speedy.com.ar}{Club
    Speedy} (Membership Reward Program of one of the largest ISPs in Argentina)
    from various PHP applications to a fully integrated site developed with
    Ruby on Rails. Responsible of meetings with the client and of designing,
    implementing and deploying the web site.
  \item Participated in the implementation of a Single Sign--On solution for
    the 3DG Platform (forum, blogs, news site, profiles, etc.) using the
    Central Authentication Service
    (\weblink{http://en.wikipedia.org/wiki/Central_Authentication_Service}{CAS})
    protocol. Tools used:
    \weblink{https://github.com/relevance/castronaut}{castronaut},
    \weblink{https://wiki.jasig.org/display/CASC/phpCAS}{phpCAS}.
  \item Installed and configured multiple GNU/Linux servers. Responsible for
    emergency response in case of failures.
  \item Participated in the hiring process interviewing candidates.
\end{itemize}
}
%
\cventry{2010}{Undergrad Teaching Assistant}
{Universidad de Buenos Aires}{Buenos Aires, Argentina}{}{%
\begin{itemize}%
  \item ``Algorithms and Programming I''
  \item ``Algorithms and Programming II''
\end{itemize}
}
%
\cventry{2009\\ Jan -- Mar}{Research Assistant}
{TU Braunschweig}{Braunschweig, Germany}{}{%
Wrote an Installation and Basic Usage Guide for the Universal Software Radio
Peripheral (\weblink{http://www.ettus.com/products}{USRP\texttrademark}) and
GNU Radio.
}
%
\cventry{2007 -- 2008\\ Jul \ \ \ \ \ Aug}{Java Developer / Consultant}
{\weblink{http://www.newtechnologies.com.ar}{New Technologies S.R.L.}}{Buenos
Aires, Argentina}{}{%
Participated in a team developing Java applications, and
worked as an internal and external consultant.
\begin{itemize}
  \item Member of a team involved in the development of a workflow based web
    application to track and optimize the Procurement Process of the
    \weblink{http://www.telefonica.com/}{``Grupo Telefónica''} in Argentina.
    Tools used: jBPM, Tapestry, Spring, Hibernate, HttpUnit (for web scraping).
  \item Implemented prototype applications on J2EE in order to evaluate the
    adoption of different technologies (Tapestry, JavaServer Faces, Hibernate,
    Spring and Mule).
  \item Elaborated slides and examples to be used in technical talks.
\end{itemize}
}
%
\cventry{2007\\ Apr -- Jun}{Security Analyst}
{\weblink{http://www.novared.cl/}{Novared S.A.} working at %
\weblink{http://www.telecom.com.ar/}{Telecom Argentina S.A.}}{Buenos Aires,
Argentina}{}{%
Implemented the security product Novell Sentinel,  providing integrated
monitoring of more than 200 devices, in order to improve Sarbanes--Oxley
compliance.
\begin{itemize}
  \item Developed agents in Novell Sentinel's proprietary language.
  \item Developed connectors responsible of collecting and transferring logs
    and events from different services to the agents, using Perl, Bash and
    J2SE.
\end{itemize}
}

\section{Contributions to FLOSS Projects}
\cvline{}{Contributed to popular FLOSS (Open--Source) projects including:}

\cvlistdoubleitem{\mbox{\weblink{http://mercurial.selenic.com/}{Mercurial}}}{%
\mbox{\weblink{http://ace.ajax.org/}{ACE (Ajax.org Text Editor)}}}
\cvlistitem{\mbox{\weblink{http://github.com/fesplugas/typus}{Typus}}}

\section{Personal Projects}
\cvskill{\mbox{\weblink{https://github.com/gkleiman/wide}{wIDE}}\\2010 --
now}{wIDE $[$Rails 3, jQuery, jQuery UI, delayed\_jobs, Mercurial, git$]$ is a
web IDE that runs in the browser, but lives in a server. It was developed for
the \weblink{http://labi.fi.uba.ar/club_robotica.html}{Robotics Club} of the
Faculty of Engineering of the UBA, and allows them to edit and compile
programs for different microcontroller architectures from anywhere, anytime. It
allows the versioning of the projects using Mercurial.}
\cvskill{\mbox{\weblink{http://yanf.sourceforge.net/}{yanf}}\\2001}{Yanf
$[$C$]$ is a deprecated news fetcher coded by me, when I was 16 and web RSS
readers were not popular. It was published under the GPL v2 license, but is no
longer functional and is still available only for nostalgic reasons.}

\section{Languages}
\cvlanguage{Spanish}{Native}{}
\cvlanguage{English}{Fluent}{First Certificate Exam (passed with grade A),
Cambridge, 2001}
\cvlanguage{German}{Fluent}{Deutsches Sprachdiplom der KMK Stufe II, 2002}

\section{Awards}
\cventry{2008}{ALEARG Scholarship}{}{granted by the German Academic Exchange
Service (DAAD) to do research work at the TU Braunschweig}{Germany}{}{}{}{}
\cventry{2001}{Argentine Chemistry Olympiads (OAQ)}{Bronze medal}{}{}{}{}

\section{Hobbies}
\cvlistitem{Travelling, active member of
\weblink{http://couchsurfing.org}{CouchSurfing}, take almost any opportunity to
travel.}
\cvlistitem{Cooking.}
\cvlistitem{Film Geek, owner of a large constantly growing library of movies.}
\cvlistitem{Tweaking and tunning my development environment, constantly
discovering new features in my favourite editor (Vim) and trying new tools.}
\cvlistitem{Document composition with \LaTeX.}
\end{document}
